\bf A Hierarchical Bayesian Approach for Modeling Infant-Mortality and Wearout Failure Modes

### 2017-05-30 paper/paper.tex
Paper, BibTek, and a few plot files edited.

As of the first quarter of 2016, Backblaze was collecting data on 63 different hard drive models.  Some drive models have been running since 2013, while others were added at a later date.  There are a total of 75,297 hard drives in operation.  The distribution of drives by model varies: some models have only have a service record for a single drive; the maximum number of service records for a single drive model is 35,860.  We can also look at the distribution of total number of failures and total time on test across all drive brand models.  As seen in Figure \ref{fig1}, some drive models contain a lot of information, while others have few failures or little time in operation.

@@

In Figure 2 we plot the Kaplan-Meier adjusted cdf for hard drive model 14 on Weibull paper.  Drive model 14 had the most observed failures of all the brands.  Each point on the plot corresponds to a hard drive failure.  Censored drives are not plotted.  Standard error bands are calculated using Greenwood's method (reference).  As mentioned in the introduction, the population of hard drives exhibits two primary failure modes.  One mode is a result of manufacturing defects, which cause early failures, known as infant mortality.  The second mode is non-defective hard drives that eventually fail due to wearout.   Evidence of at least two failure modes is seen in the Kaplan Meier plot with a kink occurring around 15,000 hours.  Therefore, fitting a single Weibull model would not be flexible enough to model the failure distribution.

\begin{figure}[H]
\centering
\includegraphics[width=.5\textwidth]{fig/mod14_KM_adj}
\caption{Truncated Adjusted Kaplan-Meier plot showing nonparametric estimate of fraction failing for drive model 14.  Dashed lines are Greenwood standard errors.}
\end{figure}

@@

Finally, the lower right panel, corresponding to Model 4, shows that, by allowing $\pi_d$ to vary by drive model, there is greater variability in the early rate of failure and, for some drive models, the forecasted fraction failing is adjusted downward. 
\\
Comment: I think I prefer to use points for Kaplan Meier.  Using the connected dots almost makes it look like another model fit, rather than the actual observed failure data.  What do you think? \\

@@

\begin{figure}[H]
    \centering
   \includegraphics[width=5.0in]{fig/B10_full.pdf}
		\caption{B10 in Years for All Drive Models \label{fig:first}} 
\end{figure}

Am wondering if we should truncate this graph at a reasonable value, perhaps .3 or .2?

\begin{figure}[H]
    \centering
   \includegraphics[width=5.0in]{fig/pi_compare.pdf}
		\caption{$\pi$ for All Drive Models \label{fig:first}} 
\end{figure}

>>>>

As of the first quarter of 2016, Backblaze was collecting data on 63 different hard drive models.  Some drive models have been running since 2013, while others were added at a later date.  There are a total of 75,297 hard drives in operation.  The distribution of drives by model varies: some models have only have a service record for a single drive whereas the maximum number of service records for a single drive model is 35,860.  Figure \ref{fig1} shows the distribution of total number of failures and total time on test for drive brand models with at least 3 failures.  As discussed later, for model identification, a minimum of 3 failures was the criterion for hard drive brands to be included in the GLFP model.

@@

In Figure 2 we plot the Kaplan-Meier adjusted cdf for hard drive model 14 on Weibull paper.  Drive model 14 had the most observed failures of all the brands.  Each point on the plot corresponds to an observed failure.  Censored drives are not plotted.  Standard error bands are calculated using Greenwood's method \cite{green}.  As mentioned in the introduction, the population of hard drives exhibits two primary failure modes.  One mode is a result of manufacturing defects, which cause early failures, known as infant mortality.  The second mode is non-defective hard drives that eventually fail due to wearout.   Evidence of at least two failure modes is seen in the Kaplan Meier plot with a kink occurring around 15,000 hours.  Therefore, fitting a single Weibull model is not flexible enough to model the failure distribution.

\begin{figure}[H]
\centering
\includegraphics[width=.5\textwidth]{fig/mod14_KM_adj}
\caption{Truncated Adjusted Kaplan-Meier plot showing nonparametric estimate of fraction failing for drive model 14.  Dashed lines are Greenwood standard errors.  Plotted on Weibull paper.}
\end{figure}

@@

Finally, the lower right panel, corresponding to Model 4, shows that, by allowing $\pi_d$ to vary by drive model, there is greater variability in the early rate of failure and, for some drive models, the forecasted fraction failing is adjusted downward.

@@

\begin{figure}[H]
\centering
 \includegraphics[width=4.0in]{fig/b10andpi.pdf}
\caption{Left: 50\% credible intervals for B10 (time in years till 10\% of the drives fail). Right: 50\% credible intervals for $\pi$ plotted on the logit scale.  Both plots are sorted based on the median value of B10.}
\label{fig4}
\end{figure}
